---
title: "Using honestlm"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using honestlm}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 4
)
```

`honestlm` keeps familiar linear model workflows, but adds guardrails around
common interpretation traps.

```{r setup}
library(honestlm)
```

## Summaries

`honest_lm()` fits a regular `lm()` object with an extra class. The estimates
are ordinary linear-model estimates, but the printed summary hides coefficient
p-values by default.

```{r summary}
fit <- honest_lm(mpg ~ wt + factor(cyl), data = mtcars)
summary(fit)
```

For categorical predictors with more than two levels, coefficient rows are
comparisons to a reference level. They are not separate tests of whether each
category, or the whole predictor, matters. If p-values are shown, the
intercept p-value stays hidden unless you ask for `intercept_p_value = TRUE`.
For post-hoc comparisons among levels, estimated marginal means are usually a
better tool.

## Sequential sums of squares

Base `anova()` for a single linear model with more than one predictor reports
sequential Type I sums of squares. `honestlm` stops by default because those
tables depend on the order of terms in the formula. For term-level tests, use
`car::Anova(model, type = 2)` or use Type III sums of squares with care.

```{r anova-refusal, error = TRUE}
anova(fit)
```

If you really want the Type I table, you can ask for it explicitly.

```{r anova-beg}
anova(fit, beg = TRUE)
```

## Broom output

If `broom` is installed, `tidy()` removes `p.value` by default and adds a
`contrast_note` column for factor contrast rows.

```{r broom, eval = requireNamespace("broom", quietly = TRUE)}
broom::tidy(fit)
```

## Model-aware plots

`geom_lm_smooth()` and `stat_lm_means()` are designed to make plots match the
linear model structure being taught.

```{r plots}
library(ggplot2)

ggplot(mtcars, aes(wt, mpg, colour = factor(cyl))) +
  geom_point() +
  geom_lm_smooth(interaction = FALSE)

ggplot(mtcars, aes(factor(cyl), mpg, colour = factor(am))) +
  geom_point() +
  stat_lm_means(interaction = FALSE)
```

Set `interaction = TRUE` when you want separate slopes or full cell means.
